### 2014-09-30 tex/abstract.tex
updating the figures in the motivation
a stab at a new abstract

One of the fundamental challenges of using symbolic execution
to analyze software has been the treatment of dynamically
allocated data.
%, i.e., programs with complex data structures with
%unbounded domains.
State-of-the-art symbolic execution techniques 
have addressed this challenge by constructing the heap \emph{lazily},
materializing objects on the concrete heap ``as needed'' and
using non-deterministic choice points to explore each feasible
concrete heap configuration. Because analysis of the materialized
heap locations relies on concrete program semantics, the lazy
initialization approach exacerbates the state space explosion
problem that limits the scalability of symbolic execution.
In this work we present a novel approach for lazy symbolic execution
of heap manipulating software which utilizes 
a fully symbolic heap constructed on-the-fly during symbolic execution.
Our approach is 1) \emph{scalable} -- it does not
create the additional points of non-determinism
introduced by existing lazy initialization techniques and it explores
each execution path only once for any given set of isomorphic heaps,
2) \emph{precise} -- at any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and
3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
and heaps resulting from loops and recursive control structures in the code. 
We report on a case-study of an implementation of our technique in the
Symbolic PathFinder tool to illustrate its scalability, precision
and expressiveness. We also discuss how test case generation -- a common
 use for symbolic execution results -- can benefit from symbolic
 execution which uses a fully symbolic heap.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated data.
State-of-the-art techniques have addressed this challenge
through the use of heap summaries and by constructing the concrete
heap ``lazily.'' In this work, we present a novel heap analysis technique
which takes inspiration from both approaches and builds exact heap summaries
lazily during symbolic execution. Our technique enables
exact analysis of program properties and
analysis of arbitrary recursive data structures. It also supports
dynamic bounds for linked data structure inputs, and
efficient sub-division of the underlying constraint problem.
We demonstrate the precision and scalability of our approach
in the Symbolic PathFinder framework for analyzing Java programs.

%and by using 
%materializing objects on the concrete heap ``as needed'' and
%using non-deterministic choice points to explore each feasible
%concrete heap configuration.

%Because analysis of the materialized
%heap locations relies on concrete program semantics, the lazy
%initialization approach exacerbates the state space explosion
%problem that limits the scalability of symbolic execution.
%In this work we present a novel approach for lazy symbolic execution
%of heap manipulating software which utilizes 
%a fully symbolic heap constructed on-the-fly during symbolic execution.
%Our approach is 1) \emph{scalable} -- it does not
%create the additional points of non-determinism
%introduced by existing lazy initialization techniques and it explores
%each execution path only once for any given set of isomorphic heaps,
%2) \emph{precise} -- at any given point during symbolic execution, 
%the symbolic heap represents the exact set of feasible
%concrete heap structures for the program under analysis, and
%3) \emph{expressive} -- the symbolic heap can represent recursive data structures 
%and heaps resulting from loops and recursive control structures in the code. 
%We report on a case-study of an implementation of our technique in the
%Symbolic PathFinder tool to illustrate its scalability, precision
%and expressiveness. We also discuss how test case generation -- a common
 %use for symbolic execution results -- can benefit from symbolic
 %execution which uses a fully symbolic heap.
